Assessing primitives performance\\ on multi-stage execution

### 2018-05-18 paper.tex
update mac results

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3856066   0.0003752957
3   0.2087539   0.0002019377
4   2.571790   0.003453254
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.6684630   0.0010425882
3   0.3648824   0.0006104112
4   3.591927   0.007633769
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.6386585   0.0100987883
3   0.8953226   0.0055539752
4   6.956865   0.041610797
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   11.6376234   0.0575507774
3   6.1978094   0.0180202851
4   17.274749  0.107117757
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   23.9578625   0.1389707435
3   10.6698346   0.0065863712
4   25.399095  0.181054897
};
      \end{axis}
    \end{tikzpicture}

   \end{subfigure}
   \subcaption*{\textbf{\LLVMMac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
\hline
  \multirow{2}{*}{\legSlangPlug} &\GCCLinux& 0.422 $\pm$ 0.0008 & 0.767 $\pm$ 0.0011 & 1.891 $\pm$ 0.0119 & 13.12 $\pm$ 0.0171  & 25.36 $\pm$ 0.1742 \\
  						&\LLVMMac& 0.386 $\pm$ 0.0004 & 0.669 $\pm$ 0.0010 & 1.639 $\pm$ 0.0101 & 11.64 $\pm$ 0.0576  & 23.96 $\pm$ 0.1390 \\
   \hline
  \multirow{2}{*}{\legSlang} &\GCCLinux& 1.029 $\pm$ 0.0046 & 1.843 $\pm$ 0.0116 & 4.041 $\pm$ 0.0611 & 17.71 $\pm$ 0.1059 & 25.43 $\pm$ 0.1621\\
 					 &\LLVMMac& 0.209 $\pm$ 0.0002 & 0.365 $\pm$ 0.0064 & 0.895 $\pm$ 0.0056 & 6.198 $\pm$ 0.0180  & 10.67 $\pm$ 0.0066 \\
   \hline
  \multirow{2}{*}{\legRTL}  &\GCCLinux& 2.429 $\pm$ 0.0029 & 3.517 $\pm$ 0.0197  & 7.122 $\pm$ 0.0105 & 18.55 $\pm$ 0.0238 & 26.76 $\pm$ 0.1861\\
 				 	&\LLVMMac & 2.572 $\pm$ 0.0035 & 3.592 $\pm$ 0.0076 & 6.957 $\pm$ 0.0416 & 17.28 $\pm$ 0.1071  & 25.40 $\pm$ 0.1811 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}

@@

\cba{Is next paragraph good ?}
We can draw the following patterns from these results:
\begin{itemize}
\item The \legSlangPlug implementation is slower than the baseline version for small strings (0,58 times slower for empty strings, 0,23 times slower for 1-character strings). This is due to the overhead of the calls to the main VM to access the object headers and the stack. On large strings, \legSlangPlug is one of the fastest implementation with 
\item The \legRTL implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the \legSlangPlug and \legSlang ones tends to decrease as the string size increases, especially for \GCCLinux. For 1000-characters strings, the \legRTL version goes 0,25 times faster than the \legSlangPlug and the \legSlang versions.
\item The set-up used (either \GCCLinux or \LLVMMac) does lead to significant differences in terms of performance for the Slang implementation. 
\end{itemize}

>>>>

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3391346   0.0006874275
3   0.9324989   0.001469945
4   3.254642   0.007910739
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.6237533   0.0012023524
3   1.6900368   0.003040773
4   5.215819   0.015275079
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.5807038   0.0092529942
3   3.2413871   0.006737660
4   8.970703   0.035921295
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   11.4096285   0.0473858056
3   10.1485203   0.032077214
4   17.642998  0.059953679
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   23.2087956   0.1788766172
3   12.9392674   0.017734225
4   24.880755  0.198267254
};
      \end{axis}
    \end{tikzpicture}

   \end{subfigure}
   \subcaption*{\textbf{\LLVMMac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
\hline
  \multirow{2}{*}{\legSlangPlug} &\GCCLinux& 0.422 $\pm$ 0.0008 & 0.767 $\pm$ 0.0011 & 1.891 $\pm$ 0.0119 & 13.12 $\pm$ 0.0171  & 25.36 $\pm$ 0.1742 \\
  						&\LLVMMac& 0.339 $\pm$ 0.0007 & 0.6238 $\pm$ 0.0012 & 1.5807 $\pm$ 0.0092 & 11.4096 $\pm$ 0.0474  & 23.21 $\pm$ 0.1789 \\
   \hline
  \multirow{2}{*}{\legSlang} &\GCCLinux& 1.029 $\pm$ 0.0046 & 1.843 $\pm$ 0.0116 & 4.041 $\pm$ 0.0611 & 17.71 $\pm$ 0.1059 & 25.43 $\pm$ 0.1621\\
 					 &\LLVMMac& 0.932 $\pm$ 0.0015 & 1.6900 $\pm$ 0.0030 & 3.241 $\pm$ 0.0067 & 10.149 $\pm$ 0.0321  & 12.939 $\pm$ 0.0177 \\
   \hline
  \multirow{2}{*}{\legRTL}  &\GCCLinux& 2.429 $\pm$ 0.0029 & 3.517 $\pm$ 0.0197  & 7.122 $\pm$ 0.0105 & 18.55 $\pm$ 0.0238 & 26.76 $\pm$ 0.1861\\
 				 	&\LLVMMac & 3.255 $\pm$ 0.0079 & 5.216 $\pm$ 0.0153 & 8.971 $\pm$ 0.0359 & 17.643 $\pm$ 0.06  & 24.881 $\pm$ 0.1983 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}

@@

\cba{Is next paragraph good ?}
We can draw the following patterns from these results:
\begin{itemize}
\item The \legSlangPlug implementation is slower than the baseline version for small strings (0,58 times slower for empty strings, 0,23 times slower for 1-character strings). This is due to the overhead of the calls to the main VM to access the object headers and the stack. On large strings, \legSlangPlug is one of the fastest implementation. 
\item The \legRTL implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the \legSlangPlug and \legSlang ones tends to decrease as the string size increases, especially for \GCCLinux. For 1000-characters strings, the \legRTL version goes 0,25 times faster than the \legSlangPlug and the \legSlang versions.
\item The set-up used (either \GCCLinux or \LLVMMac) does lead to significant differences in terms of performance for the Slang implementation. 
\end{itemize}
